### 2021-02-23 evaluation.tex
Cut down the length of the non-long version to 15 pages
by conservative, mostly cosmetic changes.

All the experiments were run on a computer with the following specification:

\begin{itemize}
\item CPU: Intel Xeon Gold 6140 (72 cores @ \SI{2.30}{GHz})
\item RAM: \SI{383}{GiB}
\item OS: Ubuntu 20.04
\item Kernel: 5.4.0-40-generic
\end{itemize}

@@

\subsubsection{Input problems}

The input problems are assumed to be specified in the \gls{cnf} or the \gls{fof} fragment
of the \acrshort{tptp} language \cite{Sutcliffe2017}.
% http://www.tptp.org/TPTP/SyntaxBNF.html
\todo{FB: Consider joining with section Problem set below.}
\Gls{fof} problems are first converted into equisatisfiable \gls{cnf} problems by \Vampire{}.
New symbols may be introduced during preprocessing,
namely due to the Tseitin transformation and Skolemization.
We denote the preprocessed \gls{cnf} problem as $P = (\Sigma, \mathit{Cl})$,
where $\Sigma$ denotes the list of all predicate and function symbols of the problem,
and $\mathit{Cl}$ denotes a set of clauses over $\Sigma$ that constitute the problem.

\subsection{Training data}

@@

\subsubsection{Problem set}
\todo[inline]{MS: mozna bych dal propagoval cinny rod a minuly cas ...}
The examples are generated by sampling the \gls{fol} part of the problem library \gls{tptp} v7.4.0 \cite{10.1007/978-3-030-29436-6_29}.
A total of \num{17053} problems formulated in \gls{fof} and \gls{cnf} are sampled.
The problems formulated in \gls{fof} are converted to \gls{cnf} by \Vampire{}.
% vampire --mode clausify
Let $\ProblemsTptp$ denote the set of all \num{17053} \gls{cnf} problems available for training and evaluation.

@@

To ensure the efficiency of the sampling, the process is interpreted as an instance of Bernoulli multi-armed bandit problem,
\todo{Cite? MS: kdyz bude dobra citace, sem by se urcite sikla:) Pri nejhorsim Sutton \& Barto to jisti.}
with the reward of a trial being 1 in case an example is produced, and 0 otherwise.
Adaptive sampling balances
exploring problems that have been tried relatively scarcely and
exploiting problems that have yielded examples relatively often.
For each problem $P \in \ProblemsTptp$,
the generator keeps track of the number of times the problem has been tried $n_P$
and the number of examples generated from that problem $s_P$.
The ratio of $s_P$ to $n_P$ corresponds to the average reward of problem $P$ observed so far.
The problems are sampled using the allocation strategy \acrshort{ucb1} \cite{Auer2002} with a parallelizing relaxation.
In each iteration, the generator samples the problem $P$ that maximizes
$$
\frac{s_P}{n_P} + \sqrt{\frac{2 \ln n}{n_P}}
$$
\todo{FB: Shrink into text to save space.}
where $n = \sum_{P \in \ProblemsTptp} n_P$ is the total number of tries on all problems.
The parallelizing relaxation means that the $s_P$ values are only updated once in \num{1000} iterations,
allowing up to \num{2000} parallel solver executions.
\todo{Explain in detail?}

@@

\subsubsection{Sample weighting}
Each of the training examples of problem $P$ contributes to the training with the weight $\frac{1}{s_P}$,
where $s_P$ is the number of examples of problem $P$ in the training set,
so that each problem contributes to the training to the same degree irrespective of the relative numbers of examples.

\iftoggle{LONG}{
\subsubsection{Metrics}
To analyze the training process,
we tracked the dynamics of three metrics on $\ProblemsTrain$ and $\ProblemsVal$:
loss, accuracy and solver performance.
The solver performance was estimated once per 10 training epochs by running \Vampire{}
on \num{1000} problems of the respective problem set
and counting the number of problems successfully solved within the time limit.
Since the accuracy is a proxy measure of solver performance and the loss is a proxy measure of the accuracy,
we are interested in generalization from loss to accuracy and from both loss and accuracy to solver performance.
Similarly, we are interested in generalization from training set to validation set.
\todo{MS: kdyz se to tady tak pekne pripravi, asi ctenar ceka, ze se to pozdeji 
nejak zuzitkuje. Pokud se rozhnodnem loss/accuracy/ATP zavislost dal nerozebirat,
asi je tu navic i tento odstavec, nebo aspon jeho cast.}
}

\subsubsection{Termination}
We run the training until the validation accuracy stopped increasing for 100 consecutive epochs.

>>>>

All the experiments were run on a computer with
the CPU Intel Xeon Gold 6140 (72 cores @ \SI{2.30}{GHz}),
\SI{383}{GiB} RAM,
the OS Ubuntu 20.04 and
the Linux kernel 5.4.0-40-generic.

@@

\subsection{Dataset preparation}

@@

\subsubsection{Base problem set}

The input problems are assumed to be specified in the \gls{cnf} or the \gls{fof} fragment
of the \acrshort{tptp} language \cite{Sutcliffe2017}.
% http://www.tptp.org/TPTP/SyntaxBNF.html
\todo{FB: Consider joining with section Problem set below.}
\Gls{fof} problems are first converted into equisatisfiable \gls{cnf} problems by \Vampire{}.
%New symbols may be introduced during preprocessing,
%namely due to the Tseitin transformation and Skolemization.
%We denote the preprocessed \gls{cnf} problem as $P = (\Sigma, \mathit{Cl})$,
%where $\Sigma$ denotes the list of all predicate and function symbols of the problem,
%and $\mathit{Cl}$ denotes a set of clauses over $\Sigma$ that constitute the problem.

The problem library \acrshort{tptp}~v7.4.0 \cite{10.1007/978-3-030-29436-6_29}
was used as the source of problems for training and evaluation of the recommender,
offering a total of \num{17053} \gls{fol} problems.
We denote the set of all the problems available for training and evaluation as $\ProblemsTptp$.

\subsubsection{Node feature extraction}

@@

To ensure the efficiency of the sampling, the process is interpreted as an instance of Bernoulli multi-armed bandit problem,
\todo{Cite? MS: kdyz bude dobra citace, sem by se urcite sikla:) Pri nejhorsim Sutton \& Barto to jisti.}
with the reward of a trial being 1 in case an example is produced, and 0 otherwise.
Adaptive sampling balances
exploring problems that have been tried relatively scarcely and
exploiting problems that have yielded examples relatively often.
For each problem $P \in \ProblemsTptp$,
the generator keeps track of the number of times the problem has been tried $n_P$
and the number of examples generated from that problem $s_P$.
The ratio of $s_P$ to $n_P$ corresponds to the average reward of problem $P$ observed so far.
The problems are sampled using the allocation strategy \acrshort{ucb1} \cite{Auer2002} with a parallelizing relaxation.
In each iteration, the generator samples the problem $P$ that maximizes
$\frac{s_P}{n_P} + \sqrt{\frac{2 \ln n}{n_P}}$,
\todo{FB: Shrink into text to save space.}
where $n = \sum_{P \in \ProblemsTptp} n_P$ is the total number of tries on all problems.
The parallelizing relaxation means that the $s_P$ values are only updated once in \num{1000} iterations,
allowing up to \num{2000} parallel solver executions.
\todo{Explain in detail?}

@@

%\subsubsection{Sample weighting}
Each of the training examples of problem $P$ contributes to the training with the weight $\frac{1}{s_P}$,
where $s_P$ is the number of examples of problem $P$ in the training set,
so that each problem contributes to the training to the same degree irrespective of the relative numbers of examples.

\iftoggle{LONG}{
%\subsubsection{Metrics}
To analyze the training process,
we tracked the dynamics of three metrics on $\ProblemsTrain$ and $\ProblemsVal$:
loss, accuracy and solver performance.
The solver performance was estimated once per 10 training epochs by running \Vampire{}
on \num{1000} problems of the respective problem set
and counting the number of problems successfully solved within the time limit.
Since the accuracy is a proxy measure of solver performance and the loss is a proxy measure of the accuracy,
we are interested in generalization from loss to accuracy and from both loss and accuracy to solver performance.
Similarly, we are interested in generalization from training set to validation set.
\todo{MS: kdyz se to tady tak pekne pripravi, asi ctenar ceka, ze se to pozdeji 
nejak zuzitkuje. Pokud se rozhnodnem loss/accuracy/ATP zavislost dal nerozebirat,
asi je tu navic i tento odstavec, nebo aspon jeho cast.}
}

%\subsubsection{Termination}
We run the training until the validation accuracy stopped increasing for 100 consecutive epochs.
